### 2016-07-03 paper/extended-example.tex

\begin{lstlisting}
Name = [A-Z][a-z]*
Initial = [A-Z] "."
Word = ([A-Z] | [a-z] | "-" | "," | ":")+
Title = Word (" " Word)*

LastCommaFirstName = Name", " Name
		(" " (Name | Initial))*
Type = "@inproceedings" | "@article" | "@book"
BibTex = Type "{" Word ","
	("" | ("title={" Title "},"))
	("" | ("author={" LastCommaFirstName
		(" and " LastCommaFirstName)* "},"))

FullName = Name (" " (Name | Initial))*
	(" " Name)
Class = "Conference Paper" | "Journal Article"
	| "Book"
EndNote = "%0 " Class "\n"
	("%A " FullName "\n")*
	("" | ("%T " Title "\n"))
	"%1 " Word "\n"

BibEndConv : BibTex <=> EndNote = ?
\end{lstlisting}

>>>>

\begin{figure}
\begin{lstlisting}
Name    = [A-Z][a-z]*
Initial = [A-Z] "."
Word    = ([A-Z] | [a-z] | "-" | "," | ":")+
Title   = Word (" " Word)*

FN      = Name", " Name (" " (Name | Initial))*
Type    = "@inproceedings" | "@article"
BibTex  = 
  Type "{" 
    Word ","
    ("" | ("title={" Title "},"))
    ("" | ("author={" FN (" and " FN)* "},")) 
  "}"

EName   = Name (" " (Name | Initial))* (" " Name)
Class   = "Conference Paper" | "Journal Article"
EndNote = "%0 " Class "\n"
	 ("%A " EName "\n")*
	 ("" | "%T TITLE")
	  "%1 " Word "\n"

BibEndConv : BibTex <=> EndNote = ?
\end{lstlisting}
\caption{Synthesis Problem: Simplified Bibtex to EndNote}
\end{figure}
